# Preface {.unnumbered}

```{r setup, include=FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = NA, fig.align = "center", fig.width = 4, fig.height = 4, message = FALSE, warning = FALSE)
library(tidyverse)
# Parallel Processing
library(doMC)
registerDoMC(cores = 20)
```

This material is from the [DataCamp](https://www.datacamp.com) course [Introduction to Statistics in R](https://app.datacamp.com/learn/courses/modeling-with-tidymodels-in-r) by Maggie Matsui.

**Course Description:** Statistics is the study of how to collect, analyze, and draw conclusions from data. It’s a hugely valuable tool that you can use to bring the future into focus and infer the answer to tons of questions. For example, what is the likelihood of someone purchasing your product, how many calls will your support team receive, and how many jeans sizes should you manufacture to fit 95% of the population? In this course, you'll use sales data to discover how to answer questions like these as you grow your statistical skills and learn how to calculate averages, use scatterplots to show the relationship between numeric values, and calculate correlation. You'll also tackle probability, the backbone of statistical reasoning, and learn how to conduct a well-designed study to draw your own conclusions from data.

Reminder to self: each `*.qmd` file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

```{r include=FALSE, eval = TRUE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown', 'caret', 
  'caTools', 'ggplot2', "ranger", "randomForest", 'tidyverse',
  'broom', 'dplyr', 'pwr', 'haven', 'simputation', 'cluster', 
  'agricolae', 'naniar', 'mice', 'tidymodels','rsample', 'recipes', 
  'parsnip', 'dials', 'tune', 'yardstick', 'workflows'), 
  'packages.bib')
```
